Active Damping of Rotating Platforms using Integral Force Feedback

### 2020-11-02 journal/paper.tex
Change figure names

% Created 2020-11-02 lun. 14:38
% Intended LaTeX compiler: pdflatex
\documentclass[10pt]{iopart}

@@

\section{Introduction}
\label{sec:orgcbd1527}
\label{sec:introduction}
There is an increasing need to reduce the undesirable vibration of many sensitive equipment.
A common method to reduce vibration is to mount the sensitive equipment on a suspended platform which attenuates the vibrations above the frequency of the suspension modes.
In order to further decrease the residual vibrations, active damping can be used for reducing the magnification of the response in the vicinity of the resonances.

@@

\section{Dynamics of Rotating Platforms}
\label{sec:org90939ec}
\label{sec:dynamics}
In order to study how the rotation does affect the use of IFF, a model of a suspended platform on top of a rotating stage is used.
Figure \ref{fig:system} represents the model schematically which is the simplest in which gyroscopic forces can be studied.

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/system.pdf}
\caption{\label{fig:system}Schematic of the studied System}
\end{figure}

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.48\linewidth}
\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
\caption{\label{fig:campbell_diagram_real} Real Part}
\end{subfigure}
\hfill
\begin{subfigure}[c]{0.48\linewidth}
\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
\caption{\label{fig:campbell_diagram_imag} Imaginary Part}
\end{subfigure}
\hfill
\caption{\label{fig:campbell_diagram}Campbell Diagram : Evolution of the complex and real parts of the system's poles as a function of the rotational speed \(\Omega\)}
\centering
\end{figure}

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.48\linewidth}
\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms}
\end{subfigure}
\hfill
\begin{subfigure}[c]{0.48\linewidth}
\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms}
\end{subfigure}
\hfill
\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\bm{G}_d\) for several rotational speed \(\Omega\)}
\centering
\end{figure}

\section{Decentralized Integral Force Feedback}
\label{sec:orgabd3121}
\label{sec:iff}
In order to apply IFF to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
As this study focuses on decentralized control, two identical controllers \(K_F\) are used to feedback each of the sensed force to its associated actuator and no attempt is made to counteract the interactions in the system.
The control diagram is schematically shown in Figure \ref{fig:control_diagram_iff}.

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/system_iff.pdf}
\caption{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/control_diagram_iff.pdf}
\caption{\label{fig:control_diagram_iff}Control Diagram for decentralized IFF}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/plant_iff_compare_rotating_speed.pdf}
\caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the dynamics from a force actuator to its collocated force sensor (\(f_u/F_u\), \(f_v/F_v\)) for several rotational speeds \(\Omega\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
\caption{\label{fig:root_locus_pure_iff}Root Locus: evolution of the closed-loop poles with increasing controller gains \(g\)}
\end{figure}

@@

\section{Integral Force Feedback with High Pass Filter}
\label{sec:orgb936693}
\label{sec:iff_hpf}
As was explained in the previous section, the instability comes in part from the high gain at low frequency caused by the pure integrators.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/loop_gain_modified_iff.pdf}
\caption{\label{fig:loop_gain_modified_iff}Modification of the loop gain with the added HFP, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
\caption{\label{fig:root_locus_modified_iff}Modification of the Root Locus with the added HPF, \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/root_locus_wi_modified_iff.pdf}
\caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\), \(\Omega = 0.1 \omega_0\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/mod_iff_damping_wi.pdf}
\caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of \(\omega_i/\omega_0\). Corresponding control gain \(g_\text{opt}\) and \(g_\text{max}\) are also shown}
\end{figure}

@@

\section{Integral Force Feedback with Parallel Springs}
\label{sec:org9c04fb0}
\label{sec:iff_kp}
In this section additional springs in parallel with the force sensors are added to counteract the negative stiffness induced by the rotation.
Such springs are schematically shown in Figure \ref{fig:system_parallel_springs} where \(k_a\) is the stiffness of the actuator and \(k_p\) the stiffness in parallel with the actuator and force sensor.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/system_parallel_springs.pdf}
\caption{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\linewidth]{figs/cedrat_xy25xs.png}
\caption{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat Technology)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/plant_iff_kp.pdf}
\caption{\label{fig:plant_iff_kp}Bode plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/root_locus_iff_kp.pdf}
\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kps.pdf}
\caption{\label{fig:root_locus_iff_kps}Comparison the Root Locus for three parallel stiffnessses \(k_p\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/opt_damp_alpha.pdf}
\caption{\label{fig:opt_damp_alpha}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
\end{figure}

\section{Comparison and Discussion}
\label{sec:org6e6cf51}
\label{sec:comparison}
Two modifications to adapt the IFF control strategy to rotating platforms have been proposed in Sections \ref{sec:iff_hpf} and \ref{sec:iff_kp}.
These two methods are now compared in terms of added damping, closed-loop compliance and transmissibility.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/comp_root_locus.pdf}
\caption{\label{fig:comp_root_locus}Root Locus for the two proposed modifications of decentralized IFF, \(\Omega = 0.1 \omega_0\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/comp_transmissibility.pdf}
\caption{\label{fig:comp_transmissibility}Comparison of the two proposed Active Damping Techniques - Transmissibility}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/comp_compliance.pdf}
\caption{\label{fig:comp_compliance}Comparison of the two proposed Active Damping Techniques - Compliance}
\end{figure}

@@

\section{Conclusion}
\label{sec:org0fc9335}
\label{sec:conclusion}

@@

\section*{Acknowledgments}
\label{sec:org45730f8}
This research benefited from a FRIA grant from the French Community of Belgium.

\section*{References}
\label{sec:org676de81}
\bibliographystyle{iopart-num}
\bibliography{ref.bib}
\end{document}

>>>>

% Created 2020-11-02 lun. 14:46
% Intended LaTeX compiler: pdflatex
\documentclass[10pt]{iopart}

@@

\section{Introduction}
\label{sec:org45302f3}
\label{sec:introduction}
There is an increasing need to reduce the undesirable vibration of many sensitive equipment.
A common method to reduce vibration is to mount the sensitive equipment on a suspended platform which attenuates the vibrations above the frequency of the suspension modes.
In order to further decrease the residual vibrations, active damping can be used for reducing the magnification of the response in the vicinity of the resonances.

@@

\section{Dynamics of Rotating Platforms}
\label{sec:org2c62ca5}
\label{sec:dynamics}
In order to study how the rotation does affect the use of IFF, a model of a suspended platform on top of a rotating stage is used.
Figure \ref{fig:system} represents the model schematically which is the simplest in which gyroscopic forces can be studied.

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/fig01.pdf}
\caption{\label{fig:system}Schematic of the studied System}
\end{figure}

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.48\linewidth}
\includegraphics[width=\linewidth]{figs/fig02a.pdf}
\caption{\label{fig:campbell_diagram_real} Real Part}
\end{subfigure}
\hfill
\begin{subfigure}[c]{0.48\linewidth}
\includegraphics[width=\linewidth]{figs/fig02b.pdf}
\caption{\label{fig:campbell_diagram_imag} Imaginary Part}
\end{subfigure}
\hfill
\caption{\label{fig:campbell_diagram}Campbell Diagram : Evolution of the complex and real parts of the system's poles as a function of the rotational speed \(\Omega\)}
\centering
\end{figure}

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.48\linewidth}
\includegraphics[width=\linewidth]{figs/fig03a.pdf}
\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms}
\end{subfigure}
\hfill
\begin{subfigure}[c]{0.48\linewidth}
\includegraphics[width=\linewidth]{figs/fig03b.pdf}
\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms}
\end{subfigure}
\hfill
\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\bm{G}_d\) for several rotational speed \(\Omega\)}
\centering
\end{figure}

\section{Decentralized Integral Force Feedback}
\label{sec:orgaa40c6a}
\label{sec:iff}
In order to apply IFF to the system, force sensors are added in series with the two actuators (Figure \ref{fig:system_iff}).
As this study focuses on decentralized control, two identical controllers \(K_F\) are used to feedback each of the sensed force to its associated actuator and no attempt is made to counteract the interactions in the system.
The control diagram is schematically shown in Figure \ref{fig:control_diagram_iff}.

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/fig04.pdf}
\caption{\label{fig:system_iff}System with added Force Sensor in series with the actuators}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/fig05.pdf}
\caption{\label{fig:control_diagram_iff}Control Diagram for decentralized IFF}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/fig06.pdf}
\caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of the dynamics from a force actuator to its collocated force sensor (\(f_u/F_u\), \(f_v/F_v\)) for several rotational speeds \(\Omega\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/fig07.pdf}
\caption{\label{fig:root_locus_pure_iff}Root Locus: evolution of the closed-loop poles with increasing controller gains \(g\)}
\end{figure}

@@

\section{Integral Force Feedback with High Pass Filter}
\label{sec:orgcc80b31}
\label{sec:iff_hpf}
As was explained in the previous section, the instability comes in part from the high gain at low frequency caused by the pure integrators.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/fig08.pdf}
\caption{\label{fig:loop_gain_modified_iff}Modification of the loop gain with the added HFP, \(g = 2\), \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/fig09.pdf}
\caption{\label{fig:root_locus_modified_iff}Modification of the Root Locus with the added HPF, \(\omega_i = 0.1 \omega_0\) and \(\Omega = 0.1 \omega_0\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/fig10.pdf}
\caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\), \(\Omega = 0.1 \omega_0\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/fig11.pdf}
\caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of \(\omega_i/\omega_0\). Corresponding control gain \(g_\text{opt}\) and \(g_\text{max}\) are also shown}
\end{figure}

@@

\section{Integral Force Feedback with Parallel Springs}
\label{sec:org7af993d}
\label{sec:iff_kp}
In this section additional springs in parallel with the force sensors are added to counteract the negative stiffness induced by the rotation.
Such springs are schematically shown in Figure \ref{fig:system_parallel_springs} where \(k_a\) is the stiffness of the actuator and \(k_p\) the stiffness in parallel with the actuator and force sensor.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/fig12.pdf}
\caption{\label{fig:system_parallel_springs}Studied system with additional springs in parallel with the actuators and force sensors}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\linewidth]{figs/fig13.pdf}
\caption{\label{fig:cedrat_xy25xs}XY Piezoelectric Stage (XY25XS from Cedrat Technology)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/fig14.pdf}
\caption{\label{fig:plant_iff_kp}Bode plot of \(f_u/F_u\) without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/fig15.pdf}
\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without parallel spring, with parallel springs with stiffness \(k_p < m \Omega^2\) and \(k_p > m \Omega^2\), \(\Omega = 0.1 \omega_0\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/fig16.pdf}
\caption{\label{fig:root_locus_iff_kps}Comparison the Root Locus for three parallel stiffnessses \(k_p\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{figs/fig17.pdf}
\caption{\label{fig:opt_damp_alpha}Optimal Damping Ratio \(\xi_\text{opt}\) and the corresponding optimal gain \(g_\text{opt}\) as a function of \(\alpha\)}
\end{figure}

\section{Comparison and Discussion}
\label{sec:orgc3da302}
\label{sec:comparison}
Two modifications to adapt the IFF control strategy to rotating platforms have been proposed in Sections \ref{sec:iff_hpf} and \ref{sec:iff_kp}.
These two methods are now compared in terms of added damping, closed-loop compliance and transmissibility.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/fig18.pdf}
\caption{\label{fig:comp_root_locus}Root Locus for the two proposed modifications of decentralized IFF, \(\Omega = 0.1 \omega_0\)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/fig19.pdf}
\caption{\label{fig:comp_transmissibility}Comparison of the two proposed Active Damping Techniques - Transmissibility}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/fig20.pdf}
\caption{\label{fig:comp_compliance}Comparison of the two proposed Active Damping Techniques - Compliance}
\end{figure}

@@

\section{Conclusion}
\label{sec:org3e5d606}
\label{sec:conclusion}

@@

\section*{Acknowledgments}
\label{sec:org2fdf2e5}
This research benefited from a FRIA grant from the French Community of Belgium.

\section*{References}
\label{sec:org684d4d0}
\bibliographystyle{iopart-num}
\bibliography{ref.bib}
\end{document}
